### 2021-03-24 Chapter-2/Chapter-2.tex
Updates from Overleaf

\subsection{Cache-level Channel}
A CPU cache are an essential part in modern computer systems. It is a faster memory to reduce the average data accesses to the main memory.
Cache channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415} rely on the time difference between cache misses and cache hits. Cache channel attacks can observe cache accesses at the level of cache sets, cache lines or other granularities. 
We introduce two common attack strategies, namely Prime+Probe and
Flush+Reload. Prime+Probe targets a single cache set. An
attacker preloads the cache set with its own data and waits until the victim
executes the program. If the victim accesses the cache set and evicts part of
the data, the attacker will experience a slow measurement. 
While Flush+Reload targets a single cache line, it requires the attacker and victim share some memory. During the ``flush'' stage, the attacker flushes the ``monitored
memory'' from the cache and waits for the victim to access the memory,
who will load the sensitive information to the cache line. In the next phase,
the attacker reloads the ``monitored memory''. By measuring the time difference
brought by cache hit and miss, the attacker can further infer the sensitive information. Some other types of side-channels target different hardware
layers other than CPU cache.

>>>>

\subsection{Cache-level Channel}
A CPU cache are an essential part in modern computer systems. It is a faster memory to reduce the average data access costs to the main memory by storing copies of data from the main memory. When a CPU reads data from a memory location, it first check the memory location in the cache. If it finds the cache stores a copy of the memory location, a cache hit occurs. Otherwise, the CPU needs to read the data from the main memory and a cache miss happens.
Cache channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415} rely on the time difference between cache misses and cache hits. Cache channel attacks can observe cache accesses at the level of cache sets, cache lines or other granularities. 
We introduce two common attack strategies, namely Prime+Probe and
Flush+Reload. Prime+Probe targets a single cache set. An
attacker preloads the cache set with its own data and waits until the victim
executes the program. If the victim accesses the cache set and evicts part of
the data, the attacker will experience a slow measurement. 
While Flush+Reload targets a single cache line, it requires the attacker and victim share some memory. During the ``flush'' stage, the attacker flushes the ``monitored
memory'' from the cache and waits for the victim to access the memory,
who will load the sensitive information to the cache line. In the next phase,
the attacker reloads the ``monitored memory''. By measuring the time difference
brought by cache hit and miss, the attacker can further infer the sensitive information. Some other types of side-channels target different hardware
layers other than CPU cache.
